---
title: "Figures for the JRSS article"
output: 
  html_document:
    toc: true
    theme: united
    number_sections: true
---


```{r,include=FALSE}
library(knitr)
opts_chunk$set(
  concordance = TRUE,
  warning = FALSE,
  cache = T,
  message = FALSE,
  echo = FALSE
)

library(tidyverse)
library(parallel)
library(fitdistrplus)
library(gridExtra)
library(BNPdensity)
library(survival)
library(ggthemes)
library(sn)
library(forcats)
```


```{r, cache=FALSE}
source('scripts/SSD_fit_functions.R')
source('scripts/fit_analysis_functions.R')
```

#Analysis on simulated data


```{r}

make_fname = function(dataset_type, idx, method){
  paste('chains_model_comparison_simulated_data/',
        dataset_type,'_', 
        idx,'_', 
        method, '.Rdata', sep = '')
}


create_funlist = function(nit){
  list('normal_ssd' = fit_normal_ssd_on_log_data, 
       'kde_ssd' = fit_kernel_mixture_ssd_on_log_data,
       'BNP_mixture_uniform_prior' = function(x) fit_BNP_mixture_ssd_on_log_data_uniform(ddat = x, mu.pz0 = 0.1, sigma.pz0 = 1.5, Nit = nit)#,       
       )
}

Var = function(x,...){
  y = length(x)
  var(x,...)*(y-1)/y
}


Sd = function(x,...){
  y = length(x)
  sd(x,...)*sqrt((y-1)/y)
}

create_normal_datasets = function(size = 10, number = 40){
  set.seed(0)
  1:number %>% 
    lapply(FUN =  function(x) rnorm(n = size, mean = 0, sd = 1))
}
create_student_datasets = function(size = 10, number = 40, df = 3, ncp = -2){
  set.seed(0)
  1:number %>% 
    lapply(FUN =  function(x) rt(n = size, df = df, ncp = ncp))
}

normalise_weights = function(unnormalized_weights){
  unnormalized_weights / sum(unnormalized_weights)
}

rmixnorm = function(n, mus, sigmas, probs) {
  if(sum(probs)!=1) stop('check all the weights')
  if (length(unique(length(mus), length(sigmas), length(probs))) != 1){
    stop('Check your number of means, sds, unnormalized_weights')
  }
  
  rmultinom(n = 1, size = n, prob = probs) %>%
    as.numeric() %>%
    (function(x) {
      mapply(FUN = function(n_, mean_, sd_) {rnorm(n_, mean_, sd_)}, x, mus, sigmas)
    }) %>%
    unlist() %>% 
    as.vector()
}

create_multimodal_datasets = function(size = 10, number = 40, mus, sigmas, unnormalized_weights) {
  set.seed(0)
  1:number %>%
    lapply(
      FUN =  function(x) {
        rmixnorm(
          n = size, mus = mus, sigmas = sigmas, probs = unnormalized_weights %>% normalise_weights
        )
      }
    )
}

library(sn)

create_skewed_normal_datasets = function(size = 10, number = 40, xi = 0, omega = 1, alpha = -3){
  set.seed(0)
  1:number %>% 
    lapply(FUN =  function(x) rsn(n = size, xi = xi, omega = omega, alpha = alpha)%>% as.numeric()) 
}

create_dataset_list = function(){
  dataset_creators_list = list('normal' = create_normal_datasets,
                               'student' = create_student_datasets,
                               'multimodal' = function(size, number) create_multimodal_datasets(size = size, number = number,
                                                                                                mus = c(-2, 5),
                                                                                                sigmas = c(1,1),
                                                                                                unnormalized_weights = c(2,4)))
  sizes = c(10,20,50,100)
  expand.grid(dataset_creators_list %>% names, sizes) %>% 
    (function(grid){
      mapply(FUN = function(creator_name, size){dataset_creators_list[[creator_name]](size = size, number = 40)}, grid$Var1, grid$Var2, SIMPLIFY = F) %>% 
        setNames(mapply(FUN = function(creator_name, size) paste(creator_name, size, sep = ''), grid$Var1, grid$Var2, SIMPLIFY = F))})
}

load_or_compute = function(dataset_type, idx, method){
  if(method%in%c('normal_ssd', 'logis_ssd', 'kde_ssd')) compute(dataset_type, idx, method)
  else{
    fname = make_fname(dataset_type, idx, method)
    if(file.exists(fname)) readRDS(fname)
    else compute_and_save_and_return(dataset_type, idx, method)
    }
}

save_if_not_present = function(dataset_type, idx, method){
  if(method%in%c('normal_ssd', 'logis_ssd', 'kde_ssd')) return()
  else{
    fname = make_fname(dataset_type, idx, method)
    if(file.exists(fname)) return()
    else compute_and_save(dataset_type, idx, method)
  }
}

compute = function(dataset_type, idx, method){
  get_data(dataset_type, idx) %>% 
    funlist[[method]]()
}

compute_and_save_and_return = function(dataset_type, idx, method){
  res = get_data(dataset_type, idx) %>% 
    funlist[[method]]()
  saveRDS(object = res, file = make_fname(dataset_type, idx, method))
  return(res)
}

compute_and_save = function(dataset_type, idx, method){
  res = get_data(dataset_type, idx) %>% 
    funlist[[method]]()
  saveRDS(object = res, file = make_fname(dataset_type, idx, method))
  return()
}

get_data = function(dataset_type, idx){
  dataset_list[[dataset_type]][[idx]]
}

fit_all_methods_on_all_the_datasets = function(dataset_list, funlist){
  
  dataset_list %>% 
    names %>% 
    lapply(FUN = function(dataset_type) expand.grid(dataset_type, 1:length(dataset_list[[dataset_type %>% as.character()]]), funlist %>% names, stringsAsFactors = F)) %>% 
    Reduce(rbind,.)  %>% 
    setNames(c('dataset_type', 'idx', 'method')) %>% 
    (function(grid){mcmapply(FUN = save_if_not_present, grid$dataset_type, grid$idx, grid$method, mc.cores = detectCores()-1)})
  
}


get_quantiles_for_all_methods = function(list_of_list_of_fits, reference_quantile, numit = 2500, ncores = 6){
  list_of_list_of_fits %>% 
    lapply(FUN = function(list_of_fits){
      list_of_fits %>% 
        mclapply(FUN = function(fit){
          fit %>% 
            thin_fit(numit = numit) %>% 
            get_quantiles(ps = 0.05, par_ = F)}, mc.cores = ncores) %>% 
        unlist() %>% 
        (function(x) {c(mean(x), 
                        quantile(x, probs = c(0.025,0.5,0.975)), 
                        Sd(x), 
                        mean(abs(x-reference_quantile)),
                        mean(x-reference_quantile),
                        reference_quantile)} ) %>% 
        t %>% 
        data.frame() %>% 
        setNames(c('Mean_estimate','infCI','med','supCI', 'std', 'Mean_absolute_bias', 'Mean_bias', 'Reference')) %>% 
        mutate(type = list_of_fits[[1]]$qmethod)
          }) %>% 
        Reduce(rbind,.)
}

get_quantile_CI_mean_length_for_all_methods = function(list_of_list_of_fits, reference_quantile, numit = 2500, ncores = 6, nbootsamples = 102){
  list_of_list_of_fits %>% 
    lapply(FUN = function(list_of_fits){
      list_of_fits %>% 
        mclapply(FUN = function(fit){
          fit %>% 
            thin_fit(numit = numit) %>% 
            get_quantiles_and_CI(p = 0.05, par_ = F, nbootsamples = nbootsamples)}, mc.cores = ncores) %>% 
        Reduce(rbind,.) %>% 
        mutate(CI_length = C_sup-C_inf) %>% 
        (function(resdf) {c(mean(resdf$HC), 
                        quantile(resdf$HC, probs = c(0.025,0.5,0.975)), 
                        Sd(resdf$HC), 
                        mean(abs(resdf$HC-reference_quantile)),
                        mean(resdf$HC-reference_quantile),
                        reference_quantile,
                        mean(resdf$CI_length),
                        quantile(resdf$CI_length, probs = c(0.025,0.5,0.975)))} ) %>% 
        t %>% 
        data.frame() %>% 
        setNames(c('Mean_estimate','infCI','med','supCI', 'std', 'Mean_absolute_bias', 'Mean_bias', 'Reference', 'Mean_CI_length','len_infCI','len_med','len_supCI')) %>% 
        mutate(type = list_of_fits[[1]]$qmethod)
          }) %>% 
        Reduce(rbind,.)
}

format_est_CI = function(est, infCI, supCI){
  c(est, infCI, supCI) %>% 
    formatC(digits = 3) %>%
    (function(x){
      paste(x[[1]], ' [',x[[2]],';',x[[3]],']', sep = '')
    })
  }

print_quantiles_for_all_methods = function(quantiles_for_all_methods){
  quantiles_for_all_methods %>% 
    mutate(Mean_estimate_and_95CI = mapply(FUN = format_est_CI, Mean_estimate, infCI, supCI)) %>% 
    dplyr::select(c(Reference, Mean_estimate_and_95CI, Mean_bias, Mean_absolute_bias, std, type)) %>% 
    kable(digits = 3)
}

print_quantiles_and_CI_length_for_all_methods = function(quantiles_and_CI_length){
  quantiles_and_CI_length %>% 
    mutate(Mean_estimate_and_95CI = mapply(FUN = format_est_CI, Mean_estimate, infCI, supCI)) %>% 
    dplyr::select(c(Reference, Mean_estimate_and_95CI, Mean_bias, Mean_absolute_bias, std, type,Mean_CI_length)) %>% 
    kable(digits = 3)
}

get_average_density_estimates = function(list_of_list_of_fits, xs = seq(-3, 3, length.out = 30), ncores = 6){
  list_of_list_of_fits %>% 
    lapply(FUN = function(list_of_fits){
      list_of_fits %>% 
        mclapply(FUN = function(fit){
          fit %>% 
            get_dens(xs = xs)}, mc.cores = ncores) %>% 
        Reduce(cbind,.) %>% 
        rowMeans %>%  
        data.frame(dens = .) %>% 
        mutate(type = list_of_fits[[1]]$qmethod, xs = xs)
          }) %>% 
        Reduce(rbind,.)
}

plot_average_density_estimates = function(average_density_estimates, reference = NULL){
  
  p = average_density_estimates %>% 
    mutate(type = factor(type, levels = unique(type) %>% sort)) %>% 
      ggplot(aes(x = xs, y = dens, colour = type)) +
    ylab('Average density estimate') +
    xlab('')
  
  if(is.null(reference)){
    p + geom_line()
  } 
  else {
    refdens = average_density_estimates$xs %>% 
      data.frame(xs = ., dens = reference(.))
    
    p + 
      geom_line(linetype = 2, size = 1.5) +
      geom_line(data = refdens, aes(x = xs, y = dens), colour = 'black', size = 1.5)
  }
  
}

cmp_ISE_fit = function(fit, reference) {
  
  estimate = function(x) get_dens(fit = fit, xs = x)
  
  integrate(function(x) (estimate(x) - reference(x))**2,
            lower = -Inf,
            upper = Inf)
}

get_MISE_for_all_methods = function(list_of_list_of_fits, reference_dist, numit = 10**6, ncores = 6){
  list_of_list_of_fits %>% 
    lapply(FUN = function(list_of_fits){
      list_of_fits %>% 
        mclapply(FUN = function(fit){cmp_ISE_fit(fit %>% thin_fit(numit = numit), reference_dist)$value}, mc.cores = ncores) %>% 
        unlist() %>% 
        (function(x) c(mean(x), quantile(x, probs = c(0.025,0.5,0.975)), Sd(x)) ) %>% 
        t %>% 
        data.frame() %>% 
        setNames(c('MISE','infCI','med','supCI', 'std')) %>% 
        mutate(type = list_of_fits[[1]]$qmethod)
          }) %>% 
        Reduce(rbind,.)
}

print_RMISE_for_all_methods = function(MISE_for_all_methods){
  MISE_for_all_methods %>% 
    mutate(Mean_MISE_and_95CI = mapply(FUN = format_est_CI, MISE, infCI, supCI)) %>% 
    (function(x){
      if ('normal_kernel_mixture_ssd'%in%x$type ){
        MISE_nkerdens = as.numeric(subset(x,type == 'normal_kernel_mixture_ssd')$MISE)
        x %>% 
          mutate(RMISE = MISE/MISE_nkerdens)
      }
        else x
    }) %>% 
    dplyr::select(c(RMISE, Mean_MISE_and_95CI, std, type)) %>% 
    kable(digits = 3)
}


save_all_models = function(fits_for_all_methods, fname){
  save(fits_for_all_methods, file = paste('chains_model_comparison_simulated_data/',fname,'.Rdata', sep = ''))
}


load_compute_or_pass = function(dataset_type, idx, method){
  if(method%in%c('normal_ssd', 'logis_ssd', 'kde_ssd')) compute(dataset_type, idx, method)
  else{
    fname = make_fname(dataset_type, idx, method)
    if(file.exists(fname)) readRDS(fname)
    else return()
    }
}

## A helper function that tests whether an object is either NULL _or_
## a list of NULLs
is.NullOb <- function(x) is.null(x) | all(sapply(x, is.null))
## Recursively step down into list, removing all such objects
rmNullObs <- function(x) {
x <- Filter(Negate(is.NullOb), x)
lapply(x, function(x) if (is.list(x)) rmNullObs(x) else x)
}

rmNull = function(list_){
  list_[!sapply(list_, is.null)]
}

get_all_fits = function(dataset_type){
  
  funlist %>% 
    names %>% 
    # .[1:3] %>% 
    lapply(FUN = function(fun){
      expand.grid(dataset_type, 1:length(dataset_list[[dataset_type %>% as.character()]]), fun, stringsAsFactors = F) %>% 
    setNames(c('dataset_type', 'idx', 'method')) %>% 
    (function(grid){mapply(FUN = load_compute_or_pass, grid$dataset_type, grid$idx, grid$method, SIMPLIFY = F)}) %>% rmNull
    })
  
}

Collect_in_a_single_file = function(dataset_type){
  res = get_all_fits(dataset_type)
  saveRDS(object = res, file = paste('chains_model_comparison_simulated_data/',dataset_type,'.Rdata', sep = ''))
}


load_file = function(dataset_type){
  readRDS(paste('chains_model_comparison_simulated_data/',dataset_type,'.Rdata', sep = ''))
}

```
```{r, eval=FALSE}
#This chunk is fairly long to run, on the order of 24h
dataset_list = create_dataset_list()
funlist = create_funlist(nit = 30000)
fit_all_methods_on_all_the_datasets(dataset_list = dataset_list, funlist = funlist)
```


```{r, eval = F}
#This is a post-processing of the result
expand.grid(c('normal', 'student', 'multimodal'), c(10,20,50,100)) %>% 
  (function(df) mapply(FUN = paste, df$Var1,df$Var2, sep = '')) %>% 
  lapply(Collect_in_a_single_file)

```


#Comparison on normal datasets
```{r}
library(knitr)
```

##Dataset of size 10

```{r, cache=F, eval=T}
rm(list = grep('fits', grep('_for_all_methods', ls(), value = T), value = T))

fits_on_normal10_for_all_methods = load_file('normal10')

```

###Mean bias on the fifth quantile

```{r, eval=T}
fits_on_normal10_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qnorm(0.05), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```


###Mean Integrated square error

```{r, eval=T}
fits_on_normal10_for_all_methods %>% 
  get_MISE_for_all_methods(reference_dist = dnorm, numit = 2500) %>% 
  print_RMISE_for_all_methods
```

###Density plot

```{r, eval=T}
fits_on_normal10_for_all_methods %>% 
  get_average_density_estimates(xs = seq(-3,3,length.out = 52)) %>% 
  plot_average_density_estimates(dnorm)
```


##Dataset of size 20

```{r, cache=F, eval=T}

rm(list = grep('fits', grep('_for_all_methods', ls(), value = T), value = T))

fits_on_normal20_for_all_methods = load_file('normal20')


```

###Mean bias on the fifth quantile


```{r, eval=T}

fits_on_normal20_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qnorm(0.05), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_normal20_for_all_methods %>% 
  get_MISE_for_all_methods(reference = dnorm, numit = 2000) %>% 
  print_RMISE_for_all_methods
```

###Density plot


```{r, eval=T}
fits_on_normal20_for_all_methods %>% 
  get_average_density_estimates(xs = seq(-3,3,length.out = 52)) %>% 
  plot_average_density_estimates(dnorm)
```


##Dataset of size 50

```{r, cache=F, eval=T}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))


fits_on_normal50_for_all_methods = load_file('normal50')


```

###Mean bias on the fifth quantile


```{r, eval=T}
fits_on_normal50_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qnorm(0.05), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_normal50_for_all_methods %>% 
  get_MISE_for_all_methods(reference = dnorm, numit = 2000) %>% 
  print_RMISE_for_all_methods
```
###Density plot


```{r, eval=T}
fits_on_normal50_for_all_methods %>% 
  get_average_density_estimates(xs = seq(-3,3,length.out = 52)) %>% 
  plot_average_density_estimates(dnorm)
```



##Dataset of size 100

```{r, cache=F}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))


fits_on_normal100_for_all_methods = load_file('normal100')


```

###Mean bias on the fifth quantile


```{r, eval=T}
fits_on_normal100_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qnorm(0.05), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_normal100_for_all_methods %>% 
  get_MISE_for_all_methods(reference = dnorm, numit = 2000) %>% 
  print_RMISE_for_all_methods
```

###Density plot


```{r, eval=T}
fits_on_normal100_for_all_methods %>% 
  get_average_density_estimates(xs = seq(-3,3,length.out = 52)) %>% 
  plot_average_density_estimates(dnorm)
```

#Comparison on student datasets

##Dataset of size 10

```{r, cache= F}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))



fits_on_student10_for_all_methods = load_file('student10')


xs_student = seq(-10,4,length.out = 52)
```

###Mean bias on the fifth quantile


```{r, eval=T}
fits_on_student10_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qt(p = 0.05, df = 3, ncp = -2), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_student10_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dt(x, df = 3, ncp = -2), numit = 2000) %>% 
  print_RMISE_for_all_methods
```

###Density plot

```{r, eval=T}
fits_on_student10_for_all_methods %>% 
  get_average_density_estimates(xs = xs_student) %>% 
  plot_average_density_estimates(function(x) dt(x, df = 3, ncp = -2))
```

##Dataset of size 20

```{r}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))

fits_on_student20_for_all_methods = load_file('student20')


```

###Mean bias on the fifth quantile


```{r, eval=T}
fits_on_student20_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qt(p = 0.05, df = 3, ncp = -2), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_student20_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dt(x, df = 3, ncp = -2), numit = 2000) %>% 
  print_RMISE_for_all_methods
```

###Density plot

```{r, eval=T}
fits_on_student20_for_all_methods %>% 
  get_average_density_estimates(xs = xs_student) %>% 
  plot_average_density_estimates(function(x) dt(x, df = 3, ncp = -2))
```

##Dataset of size 50

```{r, eval=T}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))


fits_on_student50_for_all_methods = load_file('student50')

```

###Mean bias on the fifth quantile


```{r, eval=T}
fits_on_student50_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qt(p = 0.05, df = 3, ncp = -2), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_student50_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dt(x, df = 3, ncp = -2), numit = 2000) %>% 
  print_RMISE_for_all_methods
```

###Density plot

```{r, eval=T}
fits_on_student50_for_all_methods %>% 
  get_average_density_estimates(xs = xs_student) %>% 
  plot_average_density_estimates(function(x) dt(x, df = 3, ncp = -2))
```

##Dataset of size 100

```{r}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))



fits_on_student100_for_all_methods = load_file('student100')


```

###Mean bias on the fifth quantile


```{r, eval=T}
fits_on_student100_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qt(p = 0.05, df = 3, ncp = -2), numit = 10000) %>% 
  print_quantiles_and_CI_length_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_student100_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dt(x, df = 3, ncp = -2), numit = 2000, ncores = 6) %>% 
  print_RMISE_for_all_methods
```

###Density plot

```{r, eval=T}
fits_on_student100_for_all_methods %>% 
  get_average_density_estimates(xs = xs_student, ncores = 6) %>% 
  plot_average_density_estimates(function(x) dt(x, df = 3, ncp = -2))
```

#Comparison on Multimodal normal datasets

##Dataset of size 10

```{r}
xs_multimodal = seq(-6,10,length.out = 100)

```


```{r}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))


fits_on_multimodal10_for_all_methods = load_file('multimodal10')


```

###Mean bias on the fifth quantile


```{r, eval=T}
 fits_on_multimodal10_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qmixnorm(p = 0.05, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 10000, ncores = 6) %>% 
  print_quantiles_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_multimodal10_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 2000, ncores = 6) %>% 
  print_RMISE_for_all_methods
```

###Density plot


```{r, eval=T}
fits_on_multimodal10_for_all_methods %>% 
  get_average_density_estimates(xs = xs_multimodal, ncores = 6) %>% 
  plot_average_density_estimates(function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights))
```


##Dataset of size 20

```{r}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))



fits_on_multimodal20_for_all_methods = load_file('multimodal20')


```

###Mean bias on the fifth quantile


```{r, eval=T}
 fits_on_multimodal20_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qmixnorm(p = 0.05, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 10000, ncores = 6) %>% 
  print_quantiles_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_multimodal20_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 2000, ncores = 6) %>% 
  print_RMISE_for_all_methods
```

###Density plot


```{r, eval=T}
fits_on_multimodal20_for_all_methods %>% 
  get_average_density_estimates(xs = xs_multimodal, ncores = 6) %>% 
  plot_average_density_estimates(function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights))
```


##Dataset of size 50

```{r}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))


fits_on_multimodal50_for_all_methods = load_file('multimodal50')


```

###Mean bias on the fifth quantile


```{r, eval=T}
 fits_on_multimodal50_for_all_methods %>% 
  get_quantile_CI_mean_length_for_all_methods(reference_quantile = qmixnorm(p = 0.05, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 10000, ncores = 6) %>% 
  print_quantiles_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_multimodal50_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 2000, ncores = 6) %>% 
  print_RMISE_for_all_methods
```

###Density plot


```{r, eval=T}
fits_on_multimodal50_for_all_methods %>% 
  get_average_density_estimates(xs = xs_multimodal, ncores = 6) %>% 
  plot_average_density_estimates(function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights))
```


##Dataset of size 100

```{r}

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))


fits_on_multimodal100_for_all_methods = load_file('multimodal100')


```

###Mean bias on the fifth quantile


```{r, eval=T}
 fits_on_multimodal100_for_all_methods %>% 
  get_quantiles_for_all_methods(reference_quantile = qmixnorm(p = 0.05, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 10000, ncores = 6) %>% 
  print_quantiles_for_all_methods
```

###Mean Integrated square error


```{r, eval=T}
fits_on_multimodal100_for_all_methods %>% 
  get_MISE_for_all_methods(reference = function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights), numit = 2000, ncores = 6) %>% 
  print_RMISE_for_all_methods
```

###Density plot


```{r, eval=T}
fits_on_multimodal100_for_all_methods %>% 
  get_average_density_estimates(xs = xs_multimodal, ncores = 6) %>% 
  plot_average_density_estimates(function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights))
```

## Illustration of fits and simulated data

```{r}
rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))

fits_on_normal20_for_all_methods = load_file('normal20')
xs_normal = seq(-3,3,length.out = 52)
average_density_estimates_normal20 = fits_on_normal20_for_all_methods %>% 
  get_average_density_estimates(xs = xs_normal) 
  

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))

fits_on_student20_for_all_methods = load_file('student20')
xs_student = seq(-10,4,length.out = 52)
average_density_estimates_student20 = fits_on_student20_for_all_methods %>% 
  get_average_density_estimates(xs = xs_student)

rm(list = grep('_for_all_methods', ls(), value = T) %>% grep('fits', ., value = T))

fits_on_multimodal20_for_all_methods = load_file('multimodal20')
xs_multimodal = seq(-6,10,length.out = 100)
average_density_estimates_multimodal20 = fits_on_multimodal20_for_all_methods %>% 
  get_average_density_estimates(xs = xs_multimodal)

```

```{r}
reference_grids = list(xs_normal, xs_student, xs_multimodal) %>% setNames(c("normal", "student", "multimodal"))

reference_densities = list('normal' = dnorm,
                  'student' = function(x) dt(x, df = 3, ncp = -2),
                  'multimodal' = function(x) dmixnorm(x, mus = c(-2, 5), sigmas = c(1,1), probs = c(2,4) %>% normalise_weights))

reference_densities_to_plot = reference_densities %>% 
  names %>% 
  lapply(function(nm) reference_densities[[nm]](reference_grids[[nm]]) %>% tibble(dens = ., xs = reference_grids[[nm]], data_type = paste(nm, 20))) %>% 
  bind_rows() %>% 
  mutate(data_type = stringr::str_to_title(data_type)) %>% 
  mutate(data_type = gsub(" 20", "", data_type)) %>% 
  mutate(data_type = gsub("Student", "t-Student", data_type)) %>% 
    mutate(data_type = factor(data_type, 
                            levels = c("Normal", "t-Student", "Multimodal")))
```

```{r}
average_density_estimates = rbind(average_density_estimates_normal20 %>% mutate(data_type = "Normal"),
                                  average_density_estimates_student20 %>% mutate(data_type = "t-Student"),
                                  average_density_estimates_multimodal20 %>% mutate(data_type = "Multimodal")) %>% 
  subset(!grepl("truncated_normal", type)) %>% 
  subset(!grepl("semi", type)) %>% 
  subset(!grepl("logistic", type)) %>% 
    mutate(data_type = factor(data_type, 
                            levels = c("Normal", "t-Student", "Multimodal")))

p = average_density_estimates  %>% 
    mutate(type = factor(type, levels = c("normal_ssd",  "BNP_mixture_ssd_mu0.1_sigma1.5_uniform_Gama0.4", "normal_kernel_mixture_ssd"))) %>%
  ggplot(aes(x = xs, y = dens, colour = type)) + 
  geom_line(data = reference_densities_to_plot, colour = "black") +
  geom_line(size = 1.5, linetype = 2) + 
  facet_wrap(~data_type, scales = "free") + 
  ggthemes::theme_few() + 
  ggthemes::scale_colour_few(name = 'Model type', labels = c("Normal", "BNP", "KDE")) +
  xlab("") + 
  ylab("Density") #+ 
  # 

print(p)
```

```{r}
pdf("figures/illustration_simulated_data_with_legend.pdf", width = 6*1.5, height = 2*1.5)
print(p)
dev.off()
pdf("figures/illustration_simulated_data.pdf", width = 6*1.5, height = 2*1.5)
print(p + theme(legend.position = "none"))
dev.off()
```

